The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-03-31 reviews/disc-ac1.tex
Remove TCD colors tempdiff maps from responses

The implementation of lapse-rate correction in Fig.~9 (temperature difference maps, Fig.~AC1)  results in smoother temperature difference maps, where effective temperature discrepancies are no longer overshadowed by local topographic anomalies (Fig.~AC2). Because temperature differences in this new map are much reduced, we adjusted colour scaling to emphasize smaller values (Fig.~AC3).

Also, the new Fig.~8 (temperature density maps) now uses bilinearly-interpolated temperature maps, rather than the original data (as presented in Fig.~2--4). This results in smoother density plots than those presented in the discussion paper (Fig.~AC4). In a second step, we apply a lapse-rate correction to project all reanalysis data onto the WorldClim (higher resolution) topography (Fig.~AC5). It now becomes clear that much of the discrepancies observed were due to lapse-rate effects.

For consistency, Fig.~10 (precipitation density maps) was also updated using bilinearly-interpolated data (this comment's Fig.~AC6). Note that for all density maps, colour scales were changed to allow for a higher level of detail.

@@

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+nolr+tcdc}
    \caption{Summer temperature difference maps, as in paper Fig.~9.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+tcdc}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempdiff}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$ and an updated colour mapping.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap+nolr}
    \caption{Summer temperature density maps, after bilinear interpolation.}
\end{figure}

>>>>

The implementation of lapse-rate correction in Fig.~9 (temperature difference maps, Fig.~AC1) results in smoother temperature difference maps, where effective temperature discrepancies are no longer overshadowed by local topographic anomalies (Fig.~AC2). Because temperature differences in this new map are much reduced, we adjusted colour scaling to emphasize smaller values.

Also, the new Fig.~8 (temperature density maps) now uses bilinearly-interpolated temperature maps, rather than the original data (as presented in Fig.~2--4). This results in smoother density plots than those presented in the discussion paper (Fig.~AC3). In a second step, we apply a lapse-rate correction to project all reanalysis data onto the WorldClim (higher resolution) topography (Fig.~AC4). It now becomes clear that much of the discrepancies observed were due to lapse-rate effects.

For consistency, Fig.~10 (precipitation density maps) was also updated using bilinearly-interpolated data (this comment's Fig.~AC5). Note that for all density maps, colour scales were changed to allow for a higher level of detail.

@@

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempdiff+nolr}
    \caption{Summer temperature difference maps, as in paper Fig.~9.}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=70mm]{cordillera-climate-tempdiff}
    \caption{Summer temperature difference maps, after applying a lapse-rate correction of 6\,{$^\circ$}C\,km$^{-1}$.}
\end{figure}

\begin{figure}
    \centering
    \caption{Summer temperature density maps, after bilinear interpolation.}
    \includegraphics[width=70mm]{cordillera-climate-tempheatmap+nolr}
\end{figure}
